---
title: 'Exercise for depression'
output: word_document
---

### Load libraries

```{r, message=FALSE, error=FALSE, warning=FALSE, results='hide', echo = FALSE}
# start fresh

library(tidyverse)
library(tidybayes)
library(brms)
library(readxl)
library(ggthemes)
library(ggtext)
library(ggsci)
library(cowplot)
library(MBNMAdose)
library(kableExtra)
library(ggdist)
library(patchwork)
library(ggmcmc)
library(ggridges)
library(modelr)
library(marginaleffects)
library(metafor)
library(netmeta)
library(gt)
library(PRISMA2020)
library(extrafont)


plot_theme <- ggthemes::theme_fivethirtyeight() %+replace%
    ggplot2::theme(legend.position = "none",
          text = ggplot2::element_text(family = "sans"),
          axis.title.x = ggplot2::element_text(hjust = 1, vjust = 0.5, margin = margin(t = 5, b = 5, r = 5, l = 5)),
          axis.title.y = ggplot2::element_text(vjust = 1, angle = 90, hjust = 0.5, margin = margin(t = 5, b = 5, r = 5, l = 5)),
          panel.background = ggplot2::element_blank(),
          plot.background = ggplot2::element_blank(),
          strip.background = ggplot2::element_blank(),
          legend.background = ggplot2::element_blank())
```

#### Load saved data files from bayesian analyses

```{r, message=FALSE, error=FALSE, warning=FALSE, results='hide', echo = FALSE}
### Load our dataset

#Read the analyses that we don't want to re-run
# model_by_treatment <- readRDS("model_by_treatment.RDS")
# model_by_dose <- readRDS("model_by_dose.RDS")
# model_by_length <- readRDS("model_by_length.RDS")
# model_by_intensity <- readRDS("model_by_intensity.RDS")
# model_by_lag <- readRDS("model_by_lag.RDS")
# 
# 
# moderate_by_gender <- readRDS("moderate_by_gender.RDS")
# moderate_by_age <- readRDS("moderate_by_age.RDS")
# moderate_by_depression_severity <- readRDS("moderate_by_depression_severity.RDS")
# moderate_by_comorbidities <- readRDS("moderate_by_comorbidities.RDS")
# moderate_by_group <- readRDS("moderate_by_group.RDS")
# clinician_vs_self <- readRDS("clinician_vs_self.RDS")
# funded <- readRDS("funded.RDS")
# moderate_by_nothing <- readRDS("moderate_by_nothing.RDS")
# 
# 
# one_bct_at_a_time <- readRDS("models_one_bct_at_a_time.RDS")
# mod_all_bcts <- readRDS("mod_all_bcts.RDS")
# mod_autonomy <- readRDS("mod_autonomy.RDS")
# one_rob_at_a_time <- readRDS("models_one_rob_at_a_time.RDS")
```


#### Load custom functions

```{r, message=FALSE, error=FALSE, warning=FALSE, results='hide', echo = FALSE}
d <- readRDS("data/cleaned_deprex.RDS") %>%
  rename(smd_se = se_smd)
d$class <- factor(d$class, levels = unique(d$class))
# Internal reference SD for each scale
## First, we have to know how many scales appear in our dataset

get_sd <- function(data, outcomes, outcome_num){
  #outcome_num <-  2
  #d$outcome
  return(data %>%
    filter(outcome == outcomes[outcome_num,1]) %>%
    distinct(studyID, sd_smd) %>%
    mutate(ref_sd = sum(sd_smd)/n()) %>%
    .$ref_sd %>% first() %>% as.numeric())
}

calc_ref_sds <- function(data){
  outcomes <- data %>%
    group_by(outcome) %>%
    summarise(n = n()) %>%
    arrange(desc(n)) %>%
    ungroup() %>%
    as.data.frame()

  for(i in 1:dim(outcomes)[1]){
    #i <- 2
    outcomes$sd[i] <- get_sd(data,
                             outcomes,
                             i)
  }
  return(outcomes)
}

outcomes <- calc_ref_sds(d)

# Remove acronyms and typos  from treatment names

d$trt <- gsub("CBT", "Cognitive behavioural therapy", d$trt)
d$trt <- gsub("Aerobic + Cogitive behavioural therapy", "Aerobic + Cognitive behavioural therapy", d$trt)
d$trt <- gsub("ECT", "Electroconvulsive therapy", d$trt)
d$trt <- gsub("BT", "Behaviour therapy", d$trt)
d$trt <- gsub("ACT", "Acceptance and commitment therapy", d$trt)
d$trt <- gsub("No treatment \\/ waitlist control", "Waitlist control", d$trt)

```


# Prisma diagram

```{r}

prisma_data <- PRISMA_data(read.csv("data/prisma_data.csv"))

PRISMA_save(PRISMA_flowdiagram(prisma_data),
            filename = "figs/prisma_flow.svg",
            overwrite = TRUE) 

```

# Characteristics of included studies table

```{r}
apa <- function(x, title = " ") {
  gt(x) %>%
  tab_options(
    table.border.top.color = "white",
    heading.title.font.size = px(16),
    column_labels.border.top.width = 3,
    column_labels.border.top.color = "black",
    column_labels.border.bottom.width = 3,
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table.border.bottom.color = "white",
    table.width = pct(100),
    table.background.color = "white"
  ) %>%
  cols_align(align="center") %>%
  tab_style(
    style = list(
      cell_borders(
        sides = c("top", "bottom"),
        color = "white",
        weight = px(1)
      ),
      cell_text(
        align="center"
      ),
      cell_fill(color = "white", alpha = NULL)
      ),
    locations = cells_body(
      columns = everything(),
      rows = everything()
    )
  ) %>%
    #title setup
    tab_header(
    title = html("<i>", title, "</i>")
  ) %>%
  opt_align_table_header(align = "left")
}

remove_small_arms <- function(data, threshold = 99){
 # data <- d
  small_arms <- data %>% group_by(trt) %>%
    arrange(desc(n)) %>%
    distinct(studyID, weekly_dose, .keep_all = TRUE) %>%
    summarise(n_total = sum(n)) %>% arrange(n_total) %>%
    mutate(small = n_total < threshold)
  return(data %>% filter(trt %in% small_arms$trt[!small_arms$small]))
}

# clean age variable
d$age <- gsub("\\(character\\(0\\)\\)", "(NA)", d$age)
d$age[d$age == "(NA)"] <- "NA"

# Rank severity
#unique(d$baseline_severity)
d <- mutate(d,
            baseline_severity = case_when(
              baseline_severity == "Moderately-severe" ~ "Moderate",
              baseline_severity == "Moderate–severe" ~ "Moderate",
              baseline_severity == "Mild–moderate" ~ "Mild",
              baseline_severity == "Extremely severe" ~ "Severe",
              baseline_severity == "Very severe" ~ "Severe",
              TRUE ~ baseline_severity
            ))

d$baseline_severity <- factor(d$baseline_severity,
                              ordered = TRUE,
                              levels = c("Unclear",
                                         "Mild",
                                         "Moderate",
                                         "Severe"))
  
cis_table <- d %>%
  select(studyID, country, funded,
         pre_n, pc_female, age, comorbid,
         baseline_severity, class, trt, length,
         intensity_met, weekly_dose,
         weeks_from_end_of_treatment_to_measurement,
        outcome) %>%
  arrange(tolower(studyID), class, trt, outcome, weeks_from_end_of_treatment_to_measurement) %>%
  group_by(studyID, trt, weekly_dose) %>% 
  mutate(baseline_severity = max(baseline_severity, na.rm = T),
         pre_n = max(pre_n, na.rm = T),
         outcome = paste0(unique(outcome), collapse = ", "),
         funded = ifelse(funded,"Y","N"),
         pc_female = median(round(pc_female,)),
         comorbid = ifelse(comorbid == "Reported", "Y", "N"),
         weekly_dose = round(weekly_dose, 0),
         intensity_met = round(intensity_met,),
         weeks_from_end_of_treatment_to_measurement = paste0(unique(ifelse(weeks_from_end_of_treatment_to_measurement==0,
                                                             "Post",
                                                             paste0(round(weeks_from_end_of_treatment_to_measurement,0), 
                                                                    ifelse(weeks_from_end_of_treatment_to_measurement==1,
                                                                           " week",
                                                                           " weeks")))),
                                                             collapse = ", "),
         length = round(length, 0)) %>%#filter(studyID == "Cohen-Kahn 1995")
  distinct() %>% 
  group_by(studyID) %>%
  select(-class) %>%
  rename("Author, Year" = studyID,
         Country = country,
         Funded = funded,
         n = pre_n,
         "% Female" = pc_female,
         "Mean Age (SD/Range)" = age,
         "Comorbidities" = comorbid,
         "Baseline Depression" = baseline_severity,
         "Treatment" = trt,
         "Length (weeks)" = length,
         "Exercise dose (METs/week)" = weekly_dose,
         "Intensity prescribed (METs)" = intensity_met,
         "Timepoints available" = weeks_from_end_of_treatment_to_measurement,
         "Outcomes measured" = outcome) 
cis_table %>%
  apa("Supplement 2. Characteristics of Included Studies") %>%
  gtsave("figs/Characteristics_of_Included_Studies_Table.html")

cis_table %>%
  apa("Supplement 2. Characteristics of Included Studies") %>%
  gtsave("figs/Characteristics_of_Included_Studies_Table.docx")

cis_table %>%
  ungroup() %>%
  apa("Supplement 2. Characteristics of Included Studies") %>%
  tab_options(
    ihtml.active = TRUE,
    ihtml.use_filters = TRUE,
    ihtml.use_compact_mode = FALSE,
    ihtml.use_pagination = FALSE
  ) %>% gtsave("figs/Characteristics of Included Studies Interactive.html")

## Functions for pretty results sections


library(english)
in_text <- function(num){
  if(num < 10){
    num <- as.english(num)
  } else {
    num <- format(num, big.mark=",")
  }
  num
}

gci <- function(est_data, treatment){
  #est_data <- vs_usual_care
  #treatment <- "Yoga"
  est_data %>%
    filter(trt == treatment) %>%
    mutate(summary = paste(
      "(*n* = ", format(n, big.mark = ","),
      ", *k* = ", k,
      ", *g* = ", ## also add n and k
      format(round(estimate,2), nsmall = 2),
      " [", format(round(min(c(conf.low, conf.high)),2), nsmall = 2),
      ", ", format(round(max(c(conf.low, conf.high)),2), nsmall = 2),"])",
      sep = ""
    )) %>% select(summary) %>%
    as.character() %>% return()
}

getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

indirectness_scores <- function(dat){
  #dat <- full_pairwise_data
  dat$indirect <- 1 + as.numeric(dat$comorbid=="Reported") +
    as.numeric(ifelse(is.na(dat$pc_female),
                      0,
                      dat$pc_female < 10 | dat$pc_female > 90)) +
    as.numeric(ifelse(is.na(dat$age_mean),
                      0,
                      dat$age_mean > 60 | dat$age_mean < 20))
  dat$indirect[dat$indirect>3] <- 3
  indirect <- dat %>% group_by(studyID) %>%
    summarise(indirect = max(indirect))
  dat <- dat %>% select(-indirect) %>% 
    left_join(., indirect)
  dat$indirect
}

d$indirectness <- indirectness_scores(d)

aggregate_effects <- function(dat, n = 99){
  #n <- 99
  dat <- remove_small_arms(dat, n)
  dat <- mutate(dat,
                arm_id = paste0(studyID, trt))
  dat <- escalc(data = dat,
                yi = smd,
                sei = smd_se) %>%
    aggregate(cluster = arm_id,
              rho = .6)
  dat$overall <- fct_relevel(dat$overall,
                             "High risk",
                             after = 2)
  as.data.frame(dat)
}

create_pairwise_data <- function(dat, n = 99){
  #dat <- pub_bias_data
  #n = 99
  dat <- aggregate_effects(dat, n)
  dat <- pairwise(treat = trt,
                  TE = yi,
                  seTE = sqrt(vi),
                  reference.group = "Active control",
                  studlab = studyID,
                  data = dat,
                  #n = n,
                  sm = "smd")
  dat
}

priors <- c(prior(normal(0,1), class = Intercept),
            prior(cauchy(0,1), class = sd))

active_controls <- c("Educational", "Social",
                     "Social or educational control",
                     "Usual care",
                     "Placebo pill",
                     "Stretching")
all_controls <- c(active_controls, "Waitlist control", "Active control")

### Checking the difference between control conditions before combining them

# model_by_treatment <- brm(smd | se(smd_se) ~ 1 + trt + (1 | studyID),
#                             data = remove_small_arms(d),
#                             control = list(adapt_delta = 0.99),
#                             iter = 6000,
#                             cores = 8, chains = 8,
#                             prior = priors, silent = 2)
# 
# conditional_effects(model_by_treatment)[[1]] %>% filter(trt %in% all_controls)

d <- mutate(d,
            trt = case_when(
              trt %in% active_controls ~ "Active control",
              TRUE ~ trt
            ))

if(!exists("model_by_treatment")){
  model_by_treatment <- brm(smd | se(smd_se) ~ 1 + trt + (1 | studyID),
                            data = remove_small_arms(d),
                            control = list(adapt_delta = 0.99),
                            iter = 6000,
                            cores = 8, chains = 8,
                            prior = priors, silent = 2)
  saveRDS(model_by_treatment, "model_by_treatment.RDS")
}

get_smcid <- function(data, outcomes){
  pooled_smcid <- data %>%
    group_by(outcome) %>%
    summarise(weight = n(),
              mean = mean(smd),
              sd = sd(smd),
              mcid = mean - 0.5*sd) %>% # Hengartner and Ploderl, 2022
    ungroup()
  pooled_smcid <- left_join(pooled_smcid, outcomes, by = "outcome")
  pooled_smcid$smcid <- pooled_smcid$mcid / pooled_smcid$sd.y
  # these by-hand estimated MCID values are very similar to the published in Masson and Tejani (2013)
  pooled_smcid <- pooled_smcid %>% summarise(pooled_smcid = weighted.mean(smcid, weight)) %>% as.numeric()
  return(pooled_smcid)
}

pooled_smcid <- get_smcid(d, outcomes)
active_control_est <- conditional_effects(model_by_treatment)$trt$estimate__[1]
above_active_control <- round(pooled_smcid - active_control_est, 2)

```


# Creating pairwise data and CINeMA data

CINeMA can't handle multi-level meta-analyses so use metafor's aggregate function

```{r}


one_effect_per_arm <- aggregate_effects(d)

one_effect_per_arm %>%
  mutate(rob = as.numeric(overall)) %>%
  select(studyID, trt, smd, sd_smd, n, rob, indirectness) %>%
  write.csv(.,
          "one_effect_per_arm.csv")

full_pairwise_data <- create_pairwise_data(d)

full_pairwise_model <- netmeta(full_pairwise_data,
                               common = FALSE,
                               reference.group = "Active control")
plot(full_pairwise_model,
     sortvar = names(sort(netrank(full_pairwise_model)[[1]])),
     reference.group = "Active control")

ex_arms <- c("Walking / Jogging",
             "Aerobic + Strength",
             "Aerobic",
             "Strength", 
             "Mixed aerobic exercises",
             "Cycling", "Yoga",
             "Tai-chi / Qigong", "Dance")

# Convert this to a character so it, and control arms, can be modelled
d$group_exercise[!(d$trt %in% ex_arms)] <- NA

# Set stretching to control instead of exercise
d$class[d$trt == "Active control"] <- "Control"


ex_control_pairwise <- filter(full_pairwise_data,
                              (treat1 == "Active control" | treat2 == "Active control") &
                                (treat1 %in% ex_arms | treat2 %in% ex_arms))

ex_control_pairwise$higher_favours_intervention <- ex_control_pairwise$treat1 == "Active control"
 
ex_control_pairwise$TE <- ifelse(ex_control_pairwise$higher_favours_intervention,
                                 ex_control_pairwise$TE * -1,
                                 ex_control_pairwise$TE)
  
n_per_trt <- remove_small_arms(d) %>% group_by(trt) %>%
  summarise(n = sum(n))

pts_size <- table(c(full_pairwise_model$treat1, full_pairwise_model$treat2))
pts_size <- as.data.frame(pts_size) %>% rename(trt = Var1)
pts_size <- left_join(pts_size, n_per_trt)

png(file = "figs/network_plot.png",
    width = 600*1.2, height = 600)

netmeta::netgraph(full_pairwise_model,
                  points = TRUE,
                  cex.points = pts_size$n,
                  plastic = FALSE,
                  lwd = 2,
                  offset = .04,
                  col = "darkgrey",
                  col.points = "#00B2BE",
                  alpha.transparency = .3)
dev.off()


```

Looks like the bayesian one


```{r}
full_net_split <- netsplit(full_pairwise_model)

## Assessing whether to group yoga + qigong because no difference in effects and similar mechanisms
full_net_split$indirect.random %>% filter(comparison == "Tai-chi / Qigong:Yoga")


```


### Publication bias


```{r}
# for publication bias plots compare studies with typical exercise vs typical control groups

# need publication bias estimate for all arms compared with waitlist control

pub_results <- d %>% remove_small_arms(.) %>%
  group_by(trt) %>%
  summarise(arms = unique(trt)) %>%
  filter(arms != "Active control")
  
#cycling isn't working because no significant studies

pub_results$s_value <- as.character(NA)
pub_results$eggers_p_value <- as.numeric(NA)


for(i in 1:dim(pub_results)[1]){
  #i <- 1
  pub_bias_data <- full_pairwise_data %>% filter((trt1 == "Active control" |
                                                    trt2 == "Active control") & 
                                                   (trt1 == pub_results$trt[i] |
                                                      trt2 == pub_results$trt[i]))
  if(dim(pub_bias_data)[1] >= 10 & !(pub_results$trt[i] %in% c("Cycling",
                                                              "Dance",
                                                              "Physical activity counselling",
                                                              "Waitlist control"))){
    
    
    # The pairwise function to make contrast-based dataframes can't handle
    # multiple outcomes for the same arm, or multiple uses of the same treatment
    # so calculate pooled ES for each arm
    
    pub_bias_data$higher_favours_intervention <- pub_bias_data$treat1 == "Active control"
    pub_bias_data$TE <- ifelse(pub_bias_data$higher_favours_intervention, pub_bias_data$TE * -1, pub_bias_data$TE)
    
    s_value <- PublicationBias::pubbias_svalue(yi = pub_bias_data$TE,
                                               vi = pub_bias_data$seTE^2,
                                               cluster = pub_bias_data$studyID,
                                               model_type = "robust",
                                               favor_positive = FALSE)
    summary(s_value)
    pub_results$s_value[i] <- summary(s_value)[[1]]
    
    eggers <- rma.mv(yi = TE,
                     V = seTE^2,
                     mods = ~ seTE,
                     random = ~ 1 | studyID,
                     data = pub_bias_data, test = "t")
    
    pub_results$eggers_p_value[i] <- eggers$QMp
    #summary(peese)
  }
  
}

pub_results$decision <- 1 + ifelse(is.na(pub_results$s_value),
                                   1,
                                   as.numeric(pub_results$s_value != "Not possible") + 
                                     as.numeric(pub_results$eggers_p_value < 0.05))
# No significant studies for Cycling or Waitlist so unlikely due to publication bias
pub_results$decision[pub_results$trt %in% c("Cycling","Physical activity counselling","Waitlist control")] <- 1

write.csv(pub_results, 
         "pub_bias_vs_active_controls.csv")


```



# Run BCT analyses

——Primary BCT analyses will enter each BCT, one at a time, requiring a 99% CI not overlapping zero for significance, to control for type-I error

```{r}

# The pairwise function pulls separate moderators for each arm so merge the bcts for the exercise
# condition into one column

merge_bct_columns <- function(pairwise_dat){
  #pairwise_dat <- ex_control_pairwise
  first_bct <- which(grepl('bct', names(pairwise_dat)))
  last_bct <- tail(first_bct, 1) 
  first_bct <- first_bct[1]
  #i <- first_bct
  bct_a_cols <- c(seq(first_bct,(last_bct-1), by = 2),
                  which(names(pairwise_dat) == "aut_mean1"))
  for(i in bct_a_cols){
    pairwise_dat[,i] <- ifelse(is.na(pairwise_dat[,i]),
                               pairwise_dat[,i+1],
                               pairwise_dat[,i])
  }
  new_names <- str_sub(names(pairwise_dat[,bct_a_cols]), end = -2)
  names(pairwise_dat)[bct_a_cols] <- new_names
  pairwise_dat <- pairwise_dat[, -(bct_a_cols + 1)]
  pairwise_dat
}

ex_control_pairwise <- merge_bct_columns(ex_control_pairwise)

fix_treatments <- function(pairwise_dat){
  #pairwise_dat <- ex_control_pairwise
  first_treat <- which(grepl('treat', names(pairwise_dat)))
  second_treat <- first_treat[2]
  first_treat <- first_treat[1]
  #i <- first_bct
  pairwise_dat[,first_treat] <- ifelse(pairwise_dat[,first_treat] == "Active control",
                               pairwise_dat[,second_treat],
                               pairwise_dat[,first_treat])
  names(pairwise_dat)[first_treat] <- "treat"
  pairwise_dat <- pairwise_dat[, -second_treat]
  pairwise_dat
}

ex_control_pairwise <- fix_treatments(ex_control_pairwise)

cols_valid_bcts <- ex_control_pairwise %>%
  select(contains("bct")) %>% 
  data.matrix()-1 


# find the columns where the number of studies using the BCT >= 5
cols_valid_bcts <- names(which(colSums(cols_valid_bcts) <= (dim(cols_valid_bcts)[1]-4) & 
                                 colSums(cols_valid_bcts) >= 5))
# 10_1 and 10_2 are perfectly correlated remove
# tabyl(ex_control_pairwise, bct10_1, bct10_2)
cols_valid_bcts <- cols_valid_bcts[cols_valid_bcts != "bct10_2"]

table(ex_control_pairwise$treat2)

#full_pairwise_data %>% select(any_of(cols_valid_bcts))
if(!exists("one_bct_at_a_time")){
  one_bct_at_a_time <- data.frame(estimate = NA,
                                  l99ci = NA,
                                  u99ci = NA)
  for(i in 1:length(cols_valid_bcts)){
    #i <- 13
    bct_form <- as.formula(paste0("TE | se(seTE) ~ 1 + (1 | studlab) + treat + ",
                                  cols_valid_bcts[i]))
    
    bct_fit <- brm(bct_form, data = ex_control_pairwise,
                    # control = list(adapt_delta = 0.99,
                    #                max_treedepth = 20),
                   cores = 8, chains = 8,
                   prior = priors, silent = 2)
    if(i==1){
      one_bct_at_a_time <- summary(bct_fit, prob = .99)$fixed[grepl("bct",
                                                                    rownames(summary(bct_fit,
                                                                                     prob = .99)$fixed)),
                                                              c(1,3,4)]
    } else {
      one_bct_at_a_time <- rbind(one_bct_at_a_time,
                                 summary(bct_fit, prob = .99)$fixed[grepl("bct",
                                                                    rownames(summary(bct_fit,
                                                                                     prob = .99)$fixed)),c(1,3,4)])
    }
    #summary(refm_fit, prob = .90)
  }
  saveRDS(one_bct_at_a_time, "models_one_bct_at_a_time.RDS")
}
one_bct_at_a_time <- readRDS("models_one_bct_at_a_time.RDS")
one_bct_at_a_time$bct <- rownames(one_bct_at_a_time)
library(janitor)
one_bct_at_a_time <-  clean_names(one_bct_at_a_time)
one_bct_at_a_time %>%
  mutate(bct = factor(bct, levels = one_bct_at_a_time$bct[order(one_bct_at_a_time$estimate)])) %>%
  ggplot(aes(x = bct,
             y = estimate,
             ymin = l_99_percent_ci,
             ymax = u_99_percent_ci)) +
  geom_pointrange() +
  coord_flip() + plot_theme
```

——Secondary analyses will use multiple regression (all BCTs at once):

```{r}


all_bct_form <- as.formula(paste0("TE | se(seTE) ~ 1 + (1 | studlab) + treat + ",
                              paste(cols_valid_bcts,
                                    collapse = " + ")))

if(!exists("mod_all_bcts")){
  mod_all_bcts <- brm(all_bct_form, data = ex_control_pairwise,
                      control = list(adapt_delta = 0.99,
                                      max_treedepth = 15),
                      iter = 6000,
                      cores = 8, chains = 8, prior = priors, silent = 2)
  saveRDS(mod_all_bcts, "mod_all_bcts.RDS")
}
summary(mod_all_bcts, prob = .99)
all_bcts <- summary(mod_all_bcts, prob = .99)$fixed[grepl("bct",
                                                          rownames(summary(mod_all_bcts, prob = .99)$fixed)),
                                                    c(1,3,4)] %>%
  clean_names()
all_bcts$bct <- rownames(all_bcts)
all_bcts_plot <- all_bcts %>%
  mutate(bct = factor(bct, levels = all_bcts$bct[order(all_bcts$estimate)])) %>%
  ggplot(aes(x = bct,
             y = estimate,
             ymin = l_99_percent_ci,
             ymax = u_99_percent_ci)) +
  geom_pointrange() +
  coord_flip() + plot_theme
all_bcts_plot

```

Entering all BCTs at once leaves no BCTs as significant

———machine learning classification trees using metacart and default parameters and seed(42)

```{r}
library(metacart)

# d$smd_vi <- d$sd_smd^2

ex_control_pairwise$viTE <- ex_control_pairwise$seTE ^ 2

bct_form_cart <- as.formula(paste0("TE ~ ",
                              paste(cols_valid_bcts,
                                    collapse = " + ")))


# bct_form_cart <- as.formula(paste0("smd ~ ",
#                               paste(cols_valid_bcts,
#                                     collapse = " + ")))
set.seed(42)
REtree <- REmrt(bct_form_cart,
                yi = TE,
                vi = viTE,
                data = ex_control_pairwise)

summary(REtree)
plot(REtree)
```

# Predicting effects using autonomy ratings

```{r}

if(!exists("mod_autonomy")){
  mod_autonomy <- brm("TE | se(seTE) ~ 1 + (1 | studlab) + aut_mean + treat",
                      data = ex_control_pairwise,
                      # control = list(adapt_delta = 0.99,
                      #                max_treedepth = 20),
                      cores = 8, chains = 8,
                      prior = priors, silent = 2)
  saveRDS(mod_autonomy, "mod_autonomy.RDS")
}
summary(mod_autonomy, prob = .95)
aut_plot <- conditional_effects(mod_autonomy)
aut_plot <- clean_names(aut_plot$aut_mean)


# Plotting dose-response relationship between exercise dose (METs-min/week) and effect size (SMD) 
autonomy_plot <- ggplot(aut_plot, aes(x = aut_mean,
                                    y = estimate,
                                    ymin = lower,
                                    ymax = upper)) +
  geom_ribbon(alpha = 0.3) + 
  geom_line(colour = "#0C869B") + 
  labs(x = "Degree of participant autonomy described in the method",
       y = "Predicted effect size (g)",
       fill = "Credible interval") +
  scale_x_continuous(limits = c(1, 8.5),
                     breaks = seq(1,8,1)) +
  plot_theme

ggsave(filename = "figs/S10—Moderation for level of autonomy described in the method.pdf",
        plot = autonomy_plot,
       width = 10, height = 6)


aut_plot %>% filter(aut_mean == 6) %>% select(estimate, lower, upper) %>% sapply(.,round,2)
aut_plot %>% filter(aut_mean == 1) %>% select(estimate, lower, upper) %>% sapply(.,round,2)
```

```{r}


```



# Risk of bias sensitivity analyses

## Run analyses on only low-risk studies

There was only one study with low overall risk of bias so get moderation effect for each risk of bias criteria (not in meta-regression, but in 8x simple moderation analyses)

```{r}
rob_criteria <- names(select(d, incomplete_outcome:blinding_of_personnel))
merge_unclear_high <- function(rob_col){
  rob_col <- factor(rob_col)
  levels(rob_col) <- c("Low risk",
                       "Unclear or high risk",
                       "Unclear or high risk")
  rob_col
}

rob_data <- ex_control_pairwise
rob_data[, rob_criteria] <- lapply(rob_data[, rob_criteria], merge_unclear_high)
if(!exists("one_rob_at_a_time")){
  one_rob_at_a_time <- data.frame(estimate = NA,
                                  l95ci = NA,
                                  u95ci = NA)
  for(i in 1:length(rob_criteria)){
    #i <- 8
    rob_form <- as.formula(paste0("TE | se(seTE) ~ 1 + (1 | studlab) + ",
                                  rob_criteria[i]))
    
    refm_fit <- brm(rob_form, data = rob_data,
                    # control = list(adapt_delta = 0.99,
                    #                max_treedepth = 20),
                    cores = 8, chains = 8,
                    prior = priors, silent = 2)
    get_effs <- clean_names(conditional_effects(refm_fit)[[1]])
    get_effs[,1] <- names(get_effs)[1]
    names(get_effs)[1] <- "domain"
    get_effs <- get_effs %>% select(domain, effect1, estimate, lower, upper)
    if(i==1){
      one_rob_at_a_time <- get_effs
    } else {
      one_rob_at_a_time <- rbind(one_rob_at_a_time,
                                 get_effs)
    }
    #summary(refm_fit, prob = .90)
  }
  saveRDS(one_rob_at_a_time, "models_one_rob_at_a_time.RDS")
}
sensitivity_plot <- one_rob_at_a_time %>% 
  mutate(domain = str_to_sentence(gsub("_", " ", gsub("_selection_bias", "", domain)))) %>%
  ggplot(aes(x = domain,
              y = estimate,
              ymin = lower,
              ymax = upper,
             colour = effect1)) + 
  scale_colour_manual(values = c("darkgreen", "red"))+
  geom_pointrange(position = position_dodge(width = 0.8)) + 
  geom_richtext(label = "Low risk of bias", colour = "darkgreen", x = 7.3, y = 0.2) + 
  geom_richtext(label = "Unclear or high risk of bias", colour = "red", x = 8.3, y = -0.2) + 
  xlab("Risk of bias criteria") +
  ylab("Between-group difference for exercise vs. active control") +
  coord_flip() + plot_theme
sensitivity_plot
ggsave("figs/S4—Sensitivity Analyses for Risk of Bias.pdf", width = 12, height = 6)

```


```{r}
library(robvis)

rob_figures <- full_pairwise_data %>% select(studyID,
                         random_sequence_generation_selection_bias,
                         allocation_concealment_selection_bias,
                         blinding_of_participants,
                         blinding_of_personnel,
                         blinded_outcome_assessor,
                         incomplete_outcome,
                         selective_reporting,
                         other_bias,
                         overall,
                         seTE) %>%
  mutate(Weight = as.numeric(1 / seTE^2),
         blinding_of_participants = case_when(
           blinding_of_participants == "Low risk" & 
             blinding_of_personnel == "Low risk" ~ "Low risk",
           blinding_of_participants == "High risk" ~ "High risk",
           blinding_of_personnel == "High risk" ~ "High risk",
           TRUE ~ "Unclear risk"
         )) %>%
  mutate_if(is.character,as.factor) %>%
  select(-seTE, -blinding_of_personnel) %>%
  arrange(studyID) %>% as.data.frame()

names(rob_figures) <- c("Study",
                     "Sequence generation",
                     "Allocation concealment",
                     "Blinding: participants and personnel",
                     #"Blinding: personnel",
                     "Blinding: outcome assessor",
                     "Incomplete outcome data",
                     "Selective reporting",
                     "Other bias",
                     "Overall",
                     "Weight")

# cbind(names(rob_data), names(data_rob1))
# names(rob_data) <- names(data_rob1)

getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

rob_judgments <- select(d, studyID, incomplete_outcome:blinding_of_personnel, overall) %>%
  group_by(studyID) %>%
  summarise_all(list(mode = getmode))
names(rob_judgments) <- gsub("_mode", "", names(rob_judgments))


rob_table <- rob_judgments %>%
  arrange(tolower(studyID)) %>%
  distinct() %>% 
  mutate(across(incomplete_outcome:overall,
                gsub,
                pattern = " risk",
                replacement = "")) %>%
  select(studyID,
         random_sequence_generation_selection_bias,
         allocation_concealment_selection_bias,
         blinding_of_participants,
         blinding_of_personnel,
         blinded_outcome_assessor,
         incomplete_outcome,
         selective_reporting,
         other_bias,
         overall) %>%
  rename("Author, Year" = studyID,
         "Sequence generation" = random_sequence_generation_selection_bias,
         "Allocation concealment" = allocation_concealment_selection_bias,
         "Blinding participants" = blinding_of_participants,
         "Blinding personnel" = blinding_of_personnel,
         "Blinding outcome assessment" = blinded_outcome_assessor,
         "Incomplete outcome" = incomplete_outcome,
         "Selective reporting" = selective_reporting,
         "Other bias" = other_bias,
         "Overall bias" = overall) %>%
  apa("Supplement 3. Risk of Bias in Individual Studies")
rob_table %>% gtsave("figs/Risk_of_Bias_in_Individual_Studies.html")
rob_table %>% gtsave("figs/Risk_of_Bias_in_Individual_Studies.docx")

rob_summary <- rob_summary(data = rob_figures,
                           overall = TRUE,
                           tool = "ROB1")

ggsave("figs/rob_summary.png",
       rob_summary,
       width = 10,
       height = 4)

```


## Sensitivity analyses for risk of bias criteria

```{r fig.dim = c(8, 4)}
ggsave("figs/S4—Sensitivity Analyses for Risk of Bias.pdf",
       sensitivity_plot,
       height = )
```


## Forest plot of interventions for each arm

```{r}

library(tidytext)

treatments_by_k <- remove_small_arms(d) %>% group_by(trt) %>% summarise(n = n()) %>% arrange(-n)

forest_each_arm <- remove_small_arms(d) %>% 
  mutate(studyID = factor(studyID, levels = unique(studyID)),
         ymin = round(smd - 1.96 * smd_se,2),
         ymax = round(smd + 1.96 * smd_se,2),
         smd = round(smd,2),
         trt = factor(trt,
                      levels = treatments_by_k$trt)) %>%
  ggplot(aes(x = reorder_within(studyID, smd, trt),
             y = smd,
             ymin = ymin,
             ymax = ymax,
             colour = smd,
             alpha = 100-n/max(n),
             text = trt)) +
  geom_pointrange() + plot_theme +
  scale_x_reordered() +
  xlab("Study") + 
  ylab("Hedge's g ± 95% CI") + 
  coord_flip(ylim = c(-9,4)) + 
  facet_grid(trt ~ ., scales = "free", space = "free") 
ggsave("figs/S7 Forest plot of each data point informing each arm.pdf",
       forest_each_arm,
         width = 10,
         height = 40)

forest_sample <- remove_small_arms(d) %>% 
  filter(trt == "Physical activity counselling") %>%
  mutate(studyID = factor(studyID, levels = unique(studyID)),
         ymin = round(smd - 1.96 * smd_se,2),
         ymax = round(smd + 1.96 * smd_se,2),
         smd = round(smd,2),
         trt = factor(trt,
                      levels = treatments_by_k$trt)) %>%
  ggplot(aes(x = reorder_within(studyID, smd, trt),
             y = smd,
             ymin = ymin,
             ymax = ymax,
             colour = smd,
             alpha = 100-n/max(n),
             text = trt)) +
  geom_pointrange() + plot_theme +
  scale_x_reordered() +
  xlab("Study") + 
  ylab("Hedge's g ± 95% CI") + 
  coord_flip() + 
  facet_grid(trt ~ ., scales = "free", space = "free")
ggsave("figs/Sample of arm-based forest plot.png",
       forest_sample, 
         width = 10,
         height = 3)
```




## What about the dose?


### Fitting a dose-response model

```{r, message=FALSE, warning=FALSE, error=FALSE, cache.comments=FALSE}

if(!exists("model_by_length")){
  model_by_length <- brm(smd | se(smd_se) ~ 1 + s(length, k = 4) + (1 | studyID + trt),
                       data = filter(remove_small_arms(d),
                                     class == "Exercise"),
                       control = list(adapt_delta = 0.99),
                       cores = 8, chains = 8,
                       iter = 6000,
                       prior = priors, silent = 2)
  saveRDS(model_by_length, file = "model_by_length.RDS")
}


# Fitting a prediction model 
length.data <- model_by_length %>% 
  epred_draws(newdata = expand_grid(smd_se = mean(d$smd_se),
                                    length = c(1, seq(5, 100, 5)),
                                    agent = d %>%
                                      filter(class == "Exercise") %>%
                                      .$agent %>% unique()),
              re_formula = ~ (1 | agent))

# Plotting dose-response relationship between exercise dose (METs-min/week) and effect size (SMD) 
length_plot <- ggplot(length.data, aes(x = length, y = .epred - active_control_est)) +
  stat_lineribbon(.width = .95) + 
  scale_fill_brewer(palette = "Greys") +
  geom_hline(yintercept = above_active_control, col = "red", alpha = 0.6) +
  annotate("text", x = 80, y = -0.4, label = "Clinically important difference", colour = "red") +
  labs(x = "Length of exercise program (weeks)",
       y = "Predicted effect size (g)",
       fill = "Credible interval") +
  scale_y_continuous(breaks = seq(-2, 0, .2),
                     labels = seq(-2, 0, .2),
                     limits = c(-2, 0)) +
  scale_x_continuous(breaks = c(1, seq(5, 100, 5)),
                     limits = c(1, 100)) +
  plot_theme
length_plot
ggsave(filename = "figs/S10—Moderation for intervention effects by length of intervention in weeks.pdf",
       plot = length_plot, width = 10, height = 6)

length.data %>% filter(length == 10) %>% select(`.epred`) %>% summarise_draws() %>% select(mean, q5, q95) - active_control_est

length.data %>% filter(length == 30) %>% select(`.epred`) %>% summarise_draws() %>% select(mean, q5, q95) - active_control_est
```


#### Modelling the lag length

```{r, message=FALSE, warning=FALSE, error=FALSE, cache.comments=FALSE}

hist(d$weeks_from_end_of_treatment_to_measurement)
d %>% filter(weeks_from_end_of_treatment_to_measurement > 52) %>%
  select(studyID, smd, smd_se, weeks_from_end_of_treatment_to_measurement)

d$weeks_from_end_of_treatment_to_measurement[d$weeks_from_end_of_treatment_to_measurement>52] <- 52

if(!exists("model_by_lag")){
  model_by_lag <- brm(smd | se(smd_se) ~ 1 + s(weeks_from_end_of_treatment_to_measurement, k = 4) + (1 | studyID + trt),
                       data = filter(remove_small_arms(d),
                                     class == "Exercise"),
                       control = list(adapt_delta = 0.99),
                       cores = 8, chains = 8,
                       iter = 6000,
                       prior = priors, silent = 2)
  saveRDS(model_by_lag, file = "model_by_lag.RDS")
}


# Fitting a prediction model 
lag_data <- model_by_lag %>% 
  epred_draws(newdata = expand_grid(smd_se = mean(d$smd_se),
                                    weeks_from_end_of_treatment_to_measurement = c(0, seq(1, 26, 5)),
                                    agent = d %>%
                                      filter(class == "Exercise") %>%
                                      .$agent %>% unique()),
              re_formula = ~ (1 | agent))

# Plotting dose-response relationship between exercise dose (METs-min/week) and effect size (SMD) 
lag_plot <- ggplot(lag_data, aes(x = weeks_from_end_of_treatment_to_measurement,
                                 y = .epred - active_control_est)) +
  stat_lineribbon(.width = .95) + 
  scale_fill_brewer(palette = "Greys") +
  geom_hline(yintercept = above_active_control, col = "red", alpha = 0.6) +
  annotate("text", x = 20, y = -0.4, label = "Clinically important difference", colour = "red") +
  labs(x = "Follow-up period (in weeks)",
       y = "Predicted effect size (g)",
       fill = "Credible interval") +
  scale_y_continuous(breaks = seq(-2, 0, .2),
                     labels = seq(-2, 0, .2),
                     limits = c(-2, 0)) +
  scale_x_continuous(breaks = c(0, seq(5, 26, 5)),
                     limits = c(0, 26)) +
  plot_theme
lag_plot
ggsave(filename = "figs/S11—Moderation for intervention effects by measurement lag.pdf",
       plot = lag_plot, width = 10, height = 6)
ggsave(filename = "figs/S11—Moderation for intervention effects by measurement lag.png",
       plot = lag_plot, width = 10, height = 6)

lag_data %>% filter(weeks_from_end_of_treatment_to_measurement == 0) %>% select(`.epred`) %>% summarise_draws() %>% select(mean, q5, q95) - active_control_est

lag_data %>% filter(weeks_from_end_of_treatment_to_measurement == 26) %>% select(`.epred`) %>% summarise_draws() %>% select(mean, q5, q95) - active_control_est
```


```{r, message=FALSE, warning=FALSE, error=FALSE, cache.comments=FALSE}

dose_raw <- remove_small_arms(filter(d,
                                     class == "Exercise" &
                                       !is.na(weekly_dose) &
                                       trt != "Physical activity counselling"))

if(!exists("model_by_dose")){
  model_by_dose <- brm(smd | se(smd_se) ~ 1 + s(weekly_dose, k = 4) + (1 | studyID ),
                       data = dose_raw,
                       control = list(adapt_delta = 0.99),
                       cores = 8, chains = 8,
                       iter = 6000,
                       prior = priors, silent = 2)
  saveRDS(model_by_dose, file = "model_by_dose.RDS")
}

dose_conditional <- conditional_effects(model_by_dose)
dose_conditional <- clean_names(dose_conditional$weekly_dose)

# Fitting a prediction model 
dose.data <-  dose_raw %>% 
  group_by(trt) %>%
  data_grid(smd_se = mean(d$smd_se),
            weekly_dose = seq(0, 2400, 50)) %>%
  add_epred_draws(model_by_dose,
                  ndraws = 1000,
                  re_formula = NA)



dose.data <- dose.data %>% filter(trt != "Active control") %>%
  group_by(trt) %>%
  mutate(vs_uc = .epred - active_control_est)

dose_raw %>% select(weekly_dose) %>% summarise(min = min(weekly_dose))
# Plotting dose-response relationship between exercise dose (METs-min/week) and effect size (SMD) 
dose_plot <- ggplot(dose_conditional, aes(x = weekly_dose,
                                          y = estimate - active_control_est,
                                          ymin = lower - active_control_est,
                                          ymax = upper - active_control_est)) +
  labs(x = "Dose in MET-min / week",
       y = "Predicted effect size vs. active control (Hedges' g)",
       fill = "Credible interval") +
  scale_x_continuous(breaks = c(50,seq(500, 2000, by = 500)),
                     limits = c(50, 2200)) +
  ylim(c(-2, 0.5)) +
  plot_theme + 
  annotate("rect", xmin = 500, xmax = 1000, ymin = -2, ymax = 0.5, alpha = .7, fill = "blue") +
  annotate("text", x = 750, y = 0.2, label = "WHO Guidelines", colour = "white") +
  geom_ribbon(alpha = 0.3) + 
  geom_line(colour = "#0C869B") + 
  geom_hline(yintercept = round(pooled_smcid - active_control_est,1), col = "red", alpha = 0.6) +
  annotate("text", x = 1500, y = 0, label = "Clinically important difference", colour = "red")
dose_plot
ggsave("figs/S9 Effect predicted by weekly dose in MET-min.pdf", dose_plot, width = 8, height = 4)
```

### Fitting a dose-response model for intensity
```{r, message=FALSE, warning=FALSE, error=FALSE, cache.comments=FALSE}

if(!exists("model_by_intensity")){
  model_by_intensity <- brm(smd | se(smd_se) ~ 1 + s(intensity_met, k = 4) + (1 | studyID + trt),
                       data = filter(remove_small_arms(d),
                                     class == "Exercise"),
                       control = list(adapt_delta = 0.99),
                       cores = 8, chains = 8,
                       iter = 6000,
                       prior = priors, silent = 2)
  saveRDS(model_by_intensity, file = "model_by_intensity.RDS")
}

# Fitting a prediction model 
intensity.data <- model_by_intensity %>% 
  epred_draws(newdata = expand_grid(smd_se = mean(d$smd_se),
                                    intensity_met = seq(1, 10, by = 0.2),
                                    agent = d %>%
                                      filter(class == "Exercise") %>%
                                      .$agent %>% unique()),
              re_formula = ~ (1 | agent))

# Plotting dose-response relationship between exercise dose (METs-min/week) and effect size (SMD) 
intensity_plot <- ggplot(intensity.data, aes(x = intensity_met, y = .epred - active_control_est)) +
  annotate("rect", xmin = 2.5, xmax = 4.5, ymin = -1.6, ymax = 0, alpha = .7, fill = "blue") +
  annotate("text", x = 3.5, y = -1.45, label = "Light", colour = "white") +
  annotate("text", x = 3.5, y = -1.55, label = "(e.g., walking)", colour = "white") +
  annotate("rect", xmin = 8, xmax = 10, ymin = -1.6, ymax = 0, alpha = .7, fill = "blue") +
  annotate("text", x = 9, y = -1.45, label = "Vigorous", colour = "white") +
  annotate("text", x = 9, y = -1.55, label = "(e.g., running)", colour = "white") +
  stat_lineribbon(.width = .95) + 
  scale_fill_brewer(palette = "Greys") +
  geom_hline(yintercept = round(pooled_smcid - active_control_est,1), col = "red", alpha = 0.6) +
  annotate("text", x = 6, y = -0.1, label = "Clinically important difference", colour = "red") +
  labs(x = "Intensity of exercise program (METs)",
       y = "Predicted effect size (g)",
       fill = "Credible interval") +
  scale_y_continuous(breaks = seq(-1.6, 0, .2),
                     labels = seq(-1.6, 0, .2),
                     limits = c(-1.6, 0)) +
  scale_x_continuous(breaks = seq(1, 10),
                     limits = c(1, 10)) +
  plot_theme

intensity_plot

ggsave(filename = "figs/Moderation for intervention effects by intensity of exercise in METs.png",
       plot = intensity_plot, width = 10, height = 6)

intensity.data %>% filter(intensity_met == 3) %>% select(`.epred`) %>% summarise_draws() %>% select(mean, q5, q95) - active_control_est

intensity.data %>% filter(intensity_met == 8) %>% select(`.epred`) %>% summarise_draws() %>% select(mean, q5, q95) - active_control_est

```
  
# Moderate via population characteristics

#### Gender (% female)

```{r}
if(!exists("moderate_by_gender")){
  moderate_by_gender <- brm(smd | se(smd_se) ~ 1 + trt * pc_female + (1 | studyID),
                            data = remove_small_arms(filter(d,
                                                         !is.na(pc_female)), 200),
                            control = list(adapt_delta = 0.99,
                                           max_treedepth = 15),
                            cores = 8, chains = 8,
                            iter = 6000,
                            prior = priors, silent = 2)
  saveRDS(moderate_by_gender, "moderate_by_gender.RDS")
}
summary(moderate_by_gender)
```


#### Age

```{r}

d$age_estimate <- d$age_mean
has_range_no_mean <- is.na(d$age_mean) & grepl("\\-",d$age_range_or_sd)
d$age_estimate[has_range_no_mean] <- lapply(str_split(d$age_range_or_sd[has_range_no_mean],"-"),
                                            function(x){median(as.numeric(x))}) %>% as.numeric()

table(is.na(remove_small_arms(d) %>% distinct(studyID, .keep_all = TRUE) %>% select(age_estimate)))
(1-61/(61+151))*100

if(!exists("moderate_by_age")){
  moderate_by_age <- brm(smd | se(smd_se) ~ 1 + trt * age_estimate + (1 | studyID),
                         data = remove_small_arms(filter(d,
                                                         !is.na(age_estimate)), 200),
                         control = list(adapt_delta = 0.99,
                                        max_treedepth = 15),
                         cores = 8, chains = 8,
                         iter = 6000,
                         prior = priors, silent = 2)
  saveRDS(moderate_by_age, "moderate_by_age.RDS")
}

```

#### Baseline severity

```{r}
#table(d$baseline_severity)
any_severity <- colSums(tabyl(remove_small_arms(filter(d, baseline_severity != "Unclear")),
                              baseline_severity, trt) > 1) >= 3
any_severity <- any_severity[!is.na(any_severity)]
any_severity <- names(any_severity[any_severity])

if(!exists("moderate_by_depression_severity")){
  moderate_by_depression_severity <- brm(smd | se(smd_se) ~ 1 + trt * baseline_severity + (1 | studyID),
                                         data = remove_small_arms(filter(d,
                                                                         baseline_severity != "Unclear",
                                                                         trt %in% any_severity), 200),
                                         control = list(adapt_delta = 0.99,
                                                        max_treedepth = 15),
                                         cores = 8, chains = 8,
                                         iter = 6000,
                                         prior = priors, silent = 2)
  saveRDS(moderate_by_depression_severity, "moderate_by_depression_severity.RDS")
}
```


#### Comorbidities

```{r}
janitor::tabyl(filter(remove_small_arms(d), class == "Exercise"),
      trt, comorbid)
#table(d$comorbid)
if(!exists("moderate_by_comorbidities")){
  moderate_by_comorbidities <- brm(smd | se(smd_se) ~ 1 + trt * comorbid + (1 | studyID),
                                   data = remove_small_arms(filter(d,
                                                                   !is.na(comorbid)), 200),
                                   control = list(adapt_delta = 0.99,
                                                  max_treedepth = 15),
                                   cores = 8, chains = 8,
                                   iter = 6000,
                                   prior = priors, silent = 2)
  saveRDS(moderate_by_comorbidities, "moderate_by_comorbidities.RDS")
}
```

#### Group vs. Individual programs

```{r, message=FALSE, warning=FALSE, error=FALSE, cache.comments=FALSE}

## Yoga wasn't working, check whether there are both individual and group yoga
janitor::tabyl(filter(remove_small_arms(d), class == "Exercise"),
      trt, group_exercise)

## Every yoga thing was grouped, so removed Yoga


if(!exists("moderate_by_group")){
  moderate_by_group <- brm(smd | se(smd_se) ~ 1 + trt*group_exercise + (1 | studyID),
                         data = filter(remove_small_arms(filter(d), 200),
                                     class == "Exercise",
                                     trt != "Physical activity counselling",
                                     trt != "Active control"),
                         control = list(adapt_delta = 0.99),
                         cores = 8, chains = 8,
                         iter = 6000,
                         prior = priors, silent = 2)
  saveRDS(moderate_by_group, "moderate_by_group.RDS")
}

group_conditional <- conditional_effects(moderate_by_group)

moderate_by_group_exercise <- group_conditional$`trt:group_exercise` %>%
  janitor::clean_names() %>%
  mutate(estimate = estimate - active_control_est,
         lower = lower - active_control_est,
         upper = upper - active_control_est,
         effect1 = factor(effect1, levels = unique(effect1[order(-estimate)]))) %>%
  rename(`Group Exercise` = effect2,
         Modality = effect1,
         `Effect Size`= estimate) %>%
  ggplot(aes(x = Modality, y = `Effect Size`, ymin = lower, ymax = upper,
             colour = `Group Exercise`)) +
  geom_pointrange(position = position_dodge(width = 0.5)) +
  coord_flip(ylim = c(-2,0.5)) +
  xlab("") +
  ylab("Effect on depression vs. active control (lower is better)") +
  scale_color_manual(values = c("darkgrey", "#0C869B")) + 
  plot_theme %+replace% theme(legend.position = "Right") +
    geom_richtext(label = "Individual exercise", colour = "darkgrey", x = 6.7, y = 0.2) + 
  geom_richtext(label = "Group exercise", colour = "#0C869B", x = 7.3, y = 0.2)

moderate_by_group_exercise
ggsave("figs/moderate_by_group_exercise.pdf", moderate_by_group_exercise, width = 8, height = 6)

```

#### Clinician vs. Self-reported

```{r, message=FALSE, warning=FALSE, error=FALSE, cache.comments=FALSE}

## Which arms meet our threshold for both clinician and self-reported data:

arms_with_both_reporters <- intersect(unique(remove_small_arms(filter(d,reported == "Clinician"))$trt), unique(remove_small_arms(filter(d,reported == "Self"))$trt))
## Every yoga thing was grouped, so removed Yoga


if(!exists("clinician_vs_self")){
  clinician_vs_self <- brm(smd | se(smd_se) ~ 1 + trt*reported + (1 | studyID),
                           data = filter(remove_small_arms(d), trt %in% arms_with_both_reporters),
                         control = list(adapt_delta = 0.99),
                         cores = 8, chains = 8,
                         iter = 6000,
                         prior = priors, silent = 2)
  saveRDS(clinician_vs_self, "clinician_vs_self.RDS")
}


clinician_conditional <- conditional_effects(clinician_vs_self)
clinician_reported_plot <- clinician_conditional$`trt:reported` %>%
  janitor::clean_names() %>%
  mutate(estimate = estimate - active_control_est,
         lower = lower - active_control_est,
         upper = upper - active_control_est,
         effect1 = factor(effect1, levels = unique(effect1[order(-estimate)]))) %>%
  rename(`Reported` = effect2,
         Modality = effect1,
         `Effect Size`= estimate) %>%
  ggplot(aes(x = Modality, y = `Effect Size`, ymin = lower, ymax = upper,
             colour = `Reported`)) +
  geom_pointrange(position = position_dodge(width = 0.5)) +
  coord_flip(ylim = c(-2,0.5)) +
  xlab("") +
  ylab("Effect on depression vs. active control (lower is better)") +
  scale_color_manual(values = c("Red", "Green")) + 
  plot_theme %+replace% theme(legend.position = "top")
clinician_reported_plot
ggsave("figs/moderate_by_reporter.pdf", clinician_reported_plot, width = 8, height = 6)

```


#### Moderate by funded

```{r}
d$funded_fct <- as.factor(d$funded)
tabyl(remove_small_arms(d), funded_fct, trt)
arms_with_and_without_funding <- intersect(unique(remove_small_arms(filter(d,funded))$trt), unique(remove_small_arms(filter(d,!funded))$trt))

if(!exists("funded")){
  funded <- brm(smd | se(smd_se) ~ 1 + trt*funded_fct + (1 | studyID),
                           data = remove_small_arms(filter(d,
                                                           trt %in% arms_with_and_without_funding), 200),
                         control = list(adapt_delta = 0.99),
                         cores = 8, chains = 8,
                         iter = 6000,
                         prior = priors, silent = 2)
  saveRDS(funded, "funded.RDS")
}
```


#### Combine the R2 for the moderation models

Compare them to see which to explore

```{r}
# https://bookdown.org/ajkurz/recoding_Hayes_2018/fundamentals-of-moderation-analysis.html
if(!exists("moderate_by_nothing")){
  moderate_by_nothing <- brm(smd | se(smd_se) ~ 1 + trt + (1 | studyID),
                             data = remove_small_arms(d, 200),
                             control = list(adapt_delta = 0.99,
                                            max_treedepth = 15),
                             cores = 8, chains = 8,
                             iter = 6000,
                             prior = priors, silent = 2)
  saveRDS(moderate_by_nothing, "moderate_by_nothing.RDS")
}
# compared the R2 for the base model 
r2_base <- 
  bayes_R2(moderate_by_nothing,
           summary = F) %>% 
  data.frame()

r2_gender <- 
  bayes_R2(moderate_by_gender,
           summary = F) %>% 
  data.frame()

r2_age <- 
  bayes_R2(moderate_by_age,
           summary = F) %>% 
  data.frame()

r2_depression <- 
  bayes_R2(moderate_by_depression_severity,
           summary = F) %>% 
  data.frame()

r2_comorbid <- 
  bayes_R2(moderate_by_comorbidities,
           summary = F) %>% 
  data.frame()

r2_group <- 
  bayes_R2(moderate_by_group,
           summary = F) %>% 
  data.frame()

r2_reporter <- 
  bayes_R2(clinician_vs_self,
           summary = F) %>% 
  data.frame()

r2_funded <- 
  bayes_R2(funded,
           summary = F) %>% 
  data.frame()

# here we combine them into one tibble, indexed by `model`
r2 <-
  r2_base %>% 
  bind_rows(r2_gender) %>% 
  bind_rows(r2_age) %>% 
  bind_rows(r2_depression) %>% 
  bind_rows(r2_comorbid) %>% 
  bind_rows(r2_group) %>% 
  bind_rows(r2_reporter) %>% 
  bind_rows(r2_funded) %>% 
  mutate(model = c(rep("Base", 24000),
                   rep("Gender", 24000),
                   rep("Age", 24000),
                   rep("Depression", 24000),
                   rep("Comorbid", 24000),
                   rep("Group_ex", 24000),
                   rep("Reporter", 24000),
                   rep("Funded", 24000)))

r2 %>% group_by(model) %>%
  summarise(mean = mean(R2),
            sd = sd(R2)) %>%
  arrange(mean)
# now we plot
r2_density <- r2 %>% 
  ggplot(aes(x = R2)) +
  geom_density(aes(fill = model), linewidth = 0, alpha = 2/3) +
  scale_y_continuous(NULL, breaks = NULL) +
  xlab(expression(paste(italic(R)^2, " distribution"))) +
  coord_cartesian(xlim = c(0.5, 0.8)) +# plot_theme %+replace%
  theme(legend.position = "bottom")

r2_density
ggsave("figs/S8—Density plots for R2 from models with interactions between treatment and moderators.pdf", width = 10, height = 6)
```


Gender, Age, and baseline depression appear to be moderators of intervention effects, so plot the conditional effects. Comorbidities and baseline depression only modestly improve R2, so relegate to supplementary materials.

## Conditional Effects of Age

```{r}
age_plot_data <- conditional_effects(moderate_by_age)


age_plot <- age_plot_data$`age_estimate:trt` %>%
  janitor::clean_names() %>%
  mutate(estimate = estimate - active_control_est) %>%
  rename(Age = age_estimate,
         Modality = effect2) %>%
  filter(!(Modality %in% c(all_controls,
                           "Physical activity counselling", "Cycling", "Relaxation", "SSRI", "Cognitive behavioural therapy"))) %>%
  ggplot(aes(x = Age,
             fill = Modality,
             y = estimate)) +
  geom_line(aes(colour = Modality)) + 
  facet_wrap(Modality ~ ., ncol = 2) + 
  geom_ribbon(aes(ymin = estimate - 1.96 * se,
                  ymax = estimate + 1.96 * se),
              alpha = 0.3) +
  coord_cartesian(ylim = c(-2, 0.5), xlim = c(15,70)) +
  xlab("Mean age of sample") +
  ylab("Effect on depression vs. active control (lower is better)") + 
  plot_theme + 
  theme(legend.position = "none")

ggsave("figs/modality_by_age_plot.pdf", age_plot, width = 4, height = 4)

age_plot
```

## Conditional Effects for Gender

```{r}
gender_plot_data <- conditional_effects(moderate_by_gender)
gender_plot <- gender_plot_data$`pc_female:trt` %>%
  janitor::clean_names() %>%
  mutate(estimate = estimate - active_control_est) %>%
  rename(`Percent Female` = pc_female,
         Modality = effect2) %>%
  filter(!(Modality %in% c(all_controls,
                           "Physical activity counselling", "Relaxation", "SSRI", "Cognitive behavioural therapy"))) %>%
  ggplot(aes(x = `Percent Female`,
             fill = Modality,
             y = estimate)) +
  geom_line(aes(colour = Modality)) + 
  facet_wrap(Modality ~ ., ncol = 2) + 
  coord_cartesian(ylim = c(-2, 0.5), xlim = c(0,100)) +
  geom_ribbon(aes(ymin = estimate - 1.96 * se,
                  ymax = estimate + 1.96 * se),
              alpha = 0.3) + 
  ylab("Effect on depression vs. active control (lower is better)") + 
  xlab("Percent female in the study") + plot_theme
gender_plot
ggsave("figs/modality_by_gender_plot.pdf", gender_plot, width = 4, height = 5)

library(ggpubr)
figure <- ggarrange(gender_plot, age_plot,
                    labels = c("Gender", "Age"))
ggsave("figs/age_and_gender_combined.pdf",figure, width = 12, height = 7)
ggsave("figs/age_and_gender_combined.png",figure, width = 12, height = 7)
```

#### FUNDED was big
```{r}
funded_plot <- conditional_effects(funded)
funded_plot_mod <- funded_plot$`trt:funded` %>%
  janitor::clean_names() %>%
  mutate(estimate = estimate - active_control_est,
         lower = lower - active_control_est,
         upper = upper - active_control_est,
         effect1 = factor(effect1, levels = unique(effect1[order(-estimate)]))) %>%
  rename(`Funded` = effect2,
         Modality = effect1,
         `Effect Size`= estimate) %>%
  filter(!(Modality %in% all_controls)) %>%
  ggplot(aes(x = Modality, y = `Effect Size`, ymin = lower, ymax = upper,
             colour = `Funded`)) +
  geom_pointrange(position = position_dodge(width = 0.5)) +
  coord_flip(ylim = c(-2,0.5)) +
  xlab("") +
  ylab("Effect on depression vs. active control (lower is better)") +
  #scale_color_manual(values = c("Light Blue", "Dark Blue", "Black")) + 
  plot_theme %+replace% theme(legend.position = "top")
funded_plot_mod
ggsave("figs/moderation_by_funded.pdf", funded_plot_mod, width = 8, height = 6)
```

## Conditional Effects for Different Baseline Depression Severities

```{r}
depression_plot <- conditional_effects(moderate_by_depression_severity)
moderate_by_baseline_depression <- depression_plot$`trt:baseline_severity` %>%
  janitor::clean_names() %>%
  mutate(estimate = estimate - active_control_est,
         lower = lower - active_control_est,
         upper = upper - active_control_est,
         effect1 = factor(effect1, levels = unique(effect1[order(-estimate)]))) %>%
  rename(`Baseline Severity` = effect2,
         Modality = effect1,
         `Effect Size`= estimate) %>%
  filter(!(Modality %in% all_controls)) %>%
  ggplot(aes(x = Modality, y = `Effect Size`, ymin = lower, ymax = upper,
             colour = `Baseline Severity`)) +
  geom_pointrange(position = position_dodge(width = 0.5)) +
  coord_flip(ylim = c(-2,0.5)) +
  xlab("") +
  ylab("Effect on depression vs. active control (lower is better)") +
  scale_color_manual(values = c("Light Blue", "Dark Blue", "Black")) + 
  plot_theme %+replace% theme(legend.position = "top")
moderate_by_baseline_depression
ggsave("figs/moderation_by_baseline.pdf", moderate_by_baseline_depression, width = 8, height = 6)
```

## Conditional Effects for With and Without Comorbidities

```{r}
comorbid_plot <- conditional_effects(moderate_by_comorbidities)
comorbid_plot$`trt:comorbid` %>%
  janitor::clean_names() %>%
  mutate(estimate = estimate - active_control_est,
         lower = lower - active_control_est,
         upper = upper - active_control_est) %>%
  rename(Comorbidities = effect2,
         Modality = effect1,
         `Effect Size`= estimate) %>%
  filter(!(Modality %in% all_controls)) %>%
  ggplot(aes(x = Modality, y = `Effect Size`, ymin = lower, ymax = upper,
             colour = Comorbidities)) +
  geom_pointrange(position = position_dodge(width = 0.5)) +
  coord_flip() + #ylim = c(-3,0)) +
  #plot_theme + 
  scale_color_manual(values = c("Light Blue", "Dark Blue")) + 
  theme(legend.position = "bottom")
```

# Converting effect sizes into marginal effects for comparison against usual care

```{r}
library(janitor)

conditional_effs <- conditional_effects(model_by_treatment)

vs_active_control <- conditional_effs$trt %>% clean_names() %>%
  select(trt, estimate, lower, upper) %>%
  rename(conf.high = upper,
         conf.low = lower)

# add n and k
arm_n_k <- d %>% remove_small_arms() %>%
  distinct(studyID, trt, weekly_dose, .keep_all = TRUE) %>%
  group_by(trt) %>%
  summarise(n = sum(n),
            k = n())

vs_active_control <- left_join(vs_active_control, arm_n_k, by = "trt")

full_ranks <- netrank(full_pairwise_model, method = "SUCRA", nsim = 10000)
full_ranks <- as.data.frame(full_ranks$ranking.random)
full_ranks$trt <- rownames(full_ranks)
full_ranks <- rename(full_ranks,
                     sucra = `full_ranks$ranking.random`)

vs_active_control <- left_join(vs_active_control, full_ranks, by = "trt")

new_levs <- unique(vs_active_control$trt[order(-vs_active_control$estimate)])


vs_active_control %>% filter(trt == "Active control")

vs_active_control <- vs_active_control %>%
    mutate(conf.low = conf.low - estimate[trt == "Active control"],
         conf.high = conf.high - estimate[trt == "Active control"],
         estimate = estimate - estimate[trt == "Active control"]) %>%
  filter(trt != "Active control")
  

# vs_active_control <- trt_vs_active_control %>%
#   filter(grepl("Active control", contrast)) %>%
#   rename(trt = contrast) %>%
#   mutate(trt = gsub("mean\\(Active control\\) - mean\\(", "", trt)) %>%
#   mutate(trt = gsub("\\) - mean\\(Active control\\)", "", trt)) %>%
#   mutate(trt = gsub("mean\\(", "", trt)) %>%
#   mutate(trt = gsub("\\)", "", trt)) %>%
#   mutate(contrast = "vs. Active control",
#          conf.low = ifelse(estimate > 0, conf.low * -1, conf.low),
#          conf.high = ifelse(estimate > 0, conf.high * -1, conf.high),
#          estimate = -abs(estimate)) %>%
#   select(trt, contrast, estimate, conf.low, conf.high)


# Add N
# Add k
# Add exact CI
vs_active_control$gci <- paste(format(round(vs_active_control$estimate,2), nsmall = 2),
      " [", format(round(vs_active_control$conf.low,2), nsmall = 2),
      ", ", format(round(vs_active_control$conf.high,2), nsmall = 2),"]",
      sep = "")

# Add wait list control
library(ggtext)

d %>% filter(trt == "Relaxation")

vs_active_control_plot <- vs_active_control %>%
  mutate(trt = factor(trt, levels = new_levs)) %>%
  ggplot(aes(x = trt,
             y = estimate,
             ymin = conf.low,
             ymax = conf.high)) +
  geom_pointrange(aes(colour = sucra)) +
  scale_color_continuous("blues") +
  annotate("rect", xmin = 0.5, xmax = 16.5,
           ymin = above_active_control,
           ymax = -above_active_control,
           alpha = .5, fill = "grey") +
  geom_hline(yintercept = above_active_control, col = "red", alpha = 0.4) +
  geom_hline(yintercept = -above_active_control, col = "darkgrey", alpha = 0.4) +
  geom_richtext(x = 16, y = -0.25, label = "Clinically important benefit",
                label.size = NA, colour = "red", hjust = 1 ) +
  xlab("") +
  ylab("Effect compared with active control (Hedges' g)") +
  coord_flip(xlim = c(1,16), clip = "off") + plot_theme %+replace%
  theme(plot.margin = margin(5,250,5,5)) +
  geom_text(x = vs_active_control$trt, y = 1, label = vs_active_control$gci) +
  geom_text(x = length(vs_active_control$trt)+1, y = 1, label = "g [95% CI]") +
  geom_text(x = vs_active_control$trt, y = 1.6, hjust = 1,
            label = format(vs_active_control$n, big.mark = ",")) +
  geom_text(y = -0.1, x = 8, angle = 90, colour = "white",
            label = "Equivalent to active control") +
  geom_richtext(y = 0.35, x = 8, angle = 90, colour = "grey", alpha = .3,
                label.size = NA,
            label = "Poorer outcomes / higher depression") +
  geom_text(x = length(vs_active_control$trt)+1, y = 1.55, hjust = 1, label = "n") +
  geom_text(x = vs_active_control$trt, y = 1.78, label = vs_active_control$k) +
  geom_text(x = length(vs_active_control$trt)+1, y = 1.78, label = "k") +
  geom_text(x = vs_active_control$trt, y = 2.0, label = format(round(vs_active_control$sucra,2),digits = 2)) +
  geom_text(x = length(vs_active_control$trt)+1, y = 2.0, label = "SUCRA")

ggsave("figs/figure_1_effects_vs_usual_care.png",
       vs_active_control_plot,
       dpi = "retina",
       width = 10, height = 5)

 usual_care <- summary(model_by_treatment)
# change for usual care
round(usual_care$fixed[grepl("Usualcare", rownames(usual_care$fixed)),1]+
  usual_care$fixed[grepl("Intercept", rownames(usual_care$fixed)),1],2)
# CI for usual care
round(usual_care$fixed[grepl("Usualcare", rownames(usual_care$fixed)),3]+
        usual_care$fixed[grepl("Intercept", rownames(usual_care$fixed)),1], 2)
round(usual_care$fixed[grepl("Usualcare", rownames(usual_care$fixed)),4]+
        usual_care$fixed[grepl("Intercept", rownames(usual_care$fixed)),1], 2)
# n and k
filter(arm_n_k, trt == "Usual care")
```

# Modelling acceptibility

```{r}

acceptibility_data <- remove_small_arms(d) %>%
  select(studyID, trt, n, pre_n,
         weekly_dose, intensity_met,
         overall, age_mean, pc_female, indirectness) %>%
  distinct(studyID, trt, weekly_dose, .keep_all = TRUE) %>%
  mutate(dropout = pre_n - n,
         overall = as.numeric(overall)) %>%
  group_by(studyID, trt) %>%
  summarise(pre_n = round(mean(pre_n)),
            dropout = round(mean(dropout)),
            rob = getmode(overall),
            indirectness = getmode(indirectness)) %>%
  group_by(studyID) %>%
  mutate(indirectness = getmode(indirectness))

write.csv(acceptibility_data, "data/cinema_acceptability.csv")

acceptibility_pairwise <- pairwise(treat = trt,
                                   n = pre_n,
                                   event = dropout,
                                   reference.group = "Active control",
                                   studlab = studyID,
                                   data = acceptibility_data,
                                   #n = n,
                                   sm = "OR")

netmeta_accept <- netmetabin(acceptibility_pairwise)


acceptibility_n_k <- acceptibility_data %>%
  ungroup() %>%
  filter(trt != "Dance") %>%
  distinct(studyID, trt, .keep_all = TRUE) %>%
  group_by(trt) %>%
  summarise(n = sum(pre_n),
            Dropout = sum(dropout),
            k = n())
rownames(acceptibility_n_k) <- acceptibility_n_k$trt
png(file = "figs/SXX Acceptibility by treatment.png",
    width = 600*1.2, height = 600)

forest(netmeta_accept,
       sortvar = names(sort(netrank(netmeta_accept)[[1]])),
       reference.group = "Active control",
       add.data = acceptibility_n_k,
       drop.reference.group = TRUE,
       leftcols = c("studlab","k", "n"),
       smlab = "Comparison vs Active Control\n(Mantel-Haenszel Method)")

dev.off()
```




#### Table of study/participant characteristics x treatment arm

```{r}


study_by_arm <- remove_small_arms(d) %>% group_by(trt) %>%
  rename(trt_class = class) %>%
  select(n, intensity_met, country, comorbid, baseline_severity,
         pc_female, group_exercise, weekly_dose,
         trt_class, trt, age_estimate, studyID) %>%
  distinct(studyID, trt, intensity_met, .keep_all = TRUE) %>%
  group_by(trt) %>%
  summarise(k = n(),
            n = format(sum(n), big.mark = ","),
            trt_class = getmode(trt_class),
            intensity_mean = round(mean(intensity_met, na.rm = TRUE),2),
            intensity_sd = round(sd(intensity_met, na.rm = TRUE),2),
            duration_mean = round(mean(weekly_dose/intensity_met, na.rm = TRUE),2),
            duration_sd = round(sd(weekly_dose/intensity_met, na.rm = TRUE),2),
            age_mean = round(mean(age_estimate, na.rm = TRUE), 2),
            age_sd = round(sd(age_estimate, na.rm = TRUE), 2),
            female_mean = round(mean(pc_female, na.rm = TRUE), 2),
            female_sd = round(sd(pc_female, na.rm = TRUE), 2),
            Countries = paste(sort(unique(country)), collapse = ", "),
            pc_comorbid = round(sum(comorbid == "Reported", na.rm = TRUE)/n()*100,2),
            pc_mild = round(sum(baseline_severity == "Mild", na.rm = TRUE)/n()*100,0),
            pc_moderate = round(sum(baseline_severity == "Moderate", na.rm = TRUE)/n()*100,0),
            pc_severe = round(sum(baseline_severity == "Severe", na.rm = TRUE)/n()*100,0),
            pc_group_exercise = round(sum(group_exercise == "TRUE", na.rm = TRUE)/n()*100,2)) %>%
  mutate(intensity_mean = ifelse(trt_class == "Exercise", intensity_mean, NA),
         intensity_sd = ifelse(trt_class == "Exercise", intensity_sd, NA),
         pc_group_exercise = ifelse(trt_class == "Exercise", pc_group_exercise, NA),
         Countries = gsub(" Not reported,", "", Countries),
         `Age` = ifelse(is.na(age_mean),
                      NA,
                      paste0(age_mean, " (", age_sd, ")")),
         `Percent Female` = ifelse(is.na(female_mean),
                                   NA,
                                   paste0(female_mean, " (", female_sd, ")")),
         `Intensity (METs)` = ifelse(is.na(intensity_mean),
                            NA,
                            paste0(intensity_mean, " (", intensity_sd, ")")),
         `Duration (mins/week)` = ifelse(is.na(duration_mean) | trt %in% c("Active control",
                                                                          "Waitlist control"),
                            NA,
                            paste0(duration_mean, " (", duration_sd, ")")),
         ) %>%
  select(-trt_class, -age_mean, -age_sd,
         -female_mean, -female_sd, -intensity_sd,
         -intensity_mean, -duration_mean, -duration_sd) %>%
   rename("Treatment" = trt,
          "Participants with comorbidities" = pc_comorbid,
          "Group exercise prescriptions" = pc_group_exercise,
          "Mild baseline depression" = pc_mild,
          "Moderate baseline depression" = pc_moderate,
          "Severe baseline depression" = pc_severe) %>%
  apa("Study and Participant Characteristics by Treatment Arm") |> 
  # tab_footnote(
  #   footnote = md("Numbers in parentheses are standard deviations."),
  #   locations = cells_column_labels(columns = c(`Age`, `Percent Female`, `Intensity (METs)`, `Duration (mins/week)`))
  # ) |>
  tab_spanner(
    label = "Percent of studies with",
    columns = c(
      "Participants with comorbidities",
      "Group exercise prescriptions",
      "Mild baseline depression",
      "Moderate baseline depression",
      "Severe baseline depression"
    )
  ) |>
tab_spanner(
    label = "Mean (SD)",
    columns = c(`Age`, `Percent Female`, `Intensity (METs)`, `Duration (mins/week)`)
  )

study_by_arm %>% gtsave("figs/Study and Participant Characteristics by Treatment Arm.html")
study_by_arm %>% gtsave("figs/Study and Participant Characteristics by Treatment Arm.docx")
study_by_arm |>
  tab_options(
    ihtml.active = TRUE,
    ihtml.use_filters = TRUE,
    ihtml.use_compact_mode = TRUE,
    ihtml.use_pagination = FALSE,
  ) %>% gtsave("figs/Study by Treatment Arm Interactive.html")

```




# Results
## Study Selection 
Give numbers of studies screened, assessed for eligibility, and included in the review, with reasons for exclusions at each stage, ideally with a flow diagram. 

The PRISMA flow diagram (Figure 1) outlines the study selection process. Through database searching we identified `r prisma_data$database_results` possible studies. After removing `r prisma_data$duplicates` duplicates, two reviewers independently screened each of `r prisma_data$records_screened` titles and abstracts. After screening titles and abstracts, two reviewers independently reviewed each of `r prisma_data$dbr_assessed` full-text articles. Consensus reasons for exclusion are documented in supplementary materials. Combining these new studies with the `r prisma_data$previous_studies` included in the latest Cochrane review,^19^ we included a combined total of `r prisma_data$total_studies` studies. These reviews include a combined total of `r d %>% distinct(studyID, trt, weekly_dose) %>% nrow()` arms and `r in_text(d %>% distinct(studyID, trt, weekly_dose, .keep_all = TRUE) %>% select(n) %>% sum())` participants. The characteristics of each arm in each included study are available in supplementary materials.

### Figure 1. PRISMA2020 Flow Diagram

```{r}

PRISMA_flowdiagram(prisma_data)

```


## Network Geometry

As pre-registered, we removed nodes with less than 100 participants. Following that filter, the network geometry shows most interventions contain comparisons to at least 4 other nodes (see Figure 2). Using net splitting, there was no evidence that the model violated the assumption of transitivity: there were no significant differences between effect sizes informed by direct or indirect evidence (all *p* > 0.05, *p_min_* = 0.088).

### Figure 2. Network Plot

## Risk of Bias Within Studies 
The risk of bias ratings for each study are available in supplementary materials. As shown below in Figure 3, very few studies explicitly blinded participants and personnel. As a result, most studies were unclear or high overall risk of bias, and effect sizes may include expectancy effects, among other biases. However, sensitivity analyses suggseted that effect sizes were not influenced by any risk of bias criteria (see supplementary materials).

## Figure 3. Risk of Bias Summary Plot

```{r fig.dim = c(9,3)}

rob_summary

```

## Results and Synthesis of Individual Studies

Hedges' *g* for each study is presented in a forest plot supplementary materials. The predicted effects of each treatment, when compared against usual care, is presented in Figure 4. As shown, the largest effect sizes were for dance `r gci(vs_active_control, "Dance")`, psychotherapy with aerobic exercise `r gci(vs_active_control, "Aerobic + Therapy")`, walking or jogging `r gci(vs_active_control, "Walking / Jogging")`, and strength training `r gci(vs_active_control, "Strength")`. Dance, Aerobic + CBT, and Aerobic + Behaviour Therapy were also most likely to perform best when modelling the Surface Under the Cumulative Ranking Curve (SUCRA; see supplementary materials). Consistent with other meta-analyses, there were also strong effects for CBT alone `r gci(vs_active_control, "Cognitive behavioural therapy")`, yoga `r gci(vs_active_control, "Yoga")`, and Selective Serotonin Re-uptake Inhibitors `r gci(vs_active_control, "SSRI")`.

### Figure 4. Predicted Effects of Treatments and Control Conditions, Compared Against Usual Care


The recommended modality appears to be moderated by age and gender. Compared with models that only included exercise modality (*R^2^_mean_* = `r round(mean(r2_base$R2),2)`), *R^2^* was substantially higher for models that included interactions with age (*R^2^_mean_* = `r round(mean(r2_age$R2),2)`) and gender (*R^2^_mean_* = `r round(mean(r2_gender$R2),2)`). There was no substantial increase in *R^2^* for models including baseline depression (*R^2^_mean_* = `r round(mean(r2_depression$R2),2)`) or comorbidities (*R^2^_mean_* = `r round(mean(r2_comorbid$R2),2)`). 

```{r}
round(mean(r2_reporter$R2),2)
round(mean(r2_funded$R2),2)
fun_cond <- conditional_effects(funded)
fun_cond <- clean_names(fun_cond$funded_fct) %>% select(estimate, lower, upper)
sapply(fun_cond, round, 2)


group_cond <- clean_names(group_conditional$group_exercise) %>% select(effect1, estimate, lower, upper)
sapply(group_cond[,2:4], round, 2)


```


There appeared to be larger effects from in female populations for strength training, cycling, and SSRIs. With some uncertainty, there appeared to be larger effects for men when prescribing yoga and cognitive behaviour therapy. 

### Figure 5. Effects of Interventions by Gender


Similarly, it appears that yoga and strength training were more effective for younger participants. SSRIs appeared more effect when prescribed to older participants. There is substantial uncertainty for some estimates, because some modalities were not well explored in some demographics (e.g., yoga for older adults).

### Figure 6. Effects of Interventions by Age


Across modalities, there was a modest dose-response curve for the amount prescribed per week. Prescriptions meeting or exceeding the WHO guidelines for physical activity tended to do better than lower doses, with diminishing marginal returns beyond that. Interventions lasting between 10 and 20 weeks appeared to have strongest effects, with considerable uncertainty as most studies lasted less than 20 weeks (see Supplementary Materials).

### Figure 7. Effects of Interventions by Dose, Compared with Usual Care



No behaviour change techniques significantly moderated effects. Similarly, the level of participant autonomy described in the methods did not predict effect sizes.

```{r}

PublicationBias::significance_funnel(yi = ex_control_pairwise$TE,
                                     sei = ex_control_pairwise$seTE,
                                     favor_positive = FALSE)

s_value <- PublicationBias::svalue(yi = ex_control_pairwise$TE,
                                   vi = ex_control_pairwise$seTE^2,
                                   cluster = ex_control_pairwise$studlab,
                                   q = -0.2,
                                   favor.positive = FALSE,
                                   model = "robust")

overall_ex_model <- rma.mv(yi = TE,
                           V = seTE^2,
                           data = ex_control_pairwise,
                           random = ~ 1 | studyID,
                           test = "t")

pub_bias_corrected <- rma.mv(yi = TE,
                             V = seTE^2,
                             data = ex_control_pairwise,
                             mods = seTE,
                             random = ~ 1 | studyID,
                             test = "t")

```


## Risk of Bias Across Studies 

There was evidence of some publication bias but not enough to nullify effects. The multilevel eggers was significant (F(1, `r pub_bias_corrected$QMdf[2]`) = `r round(pub_bias_corrected$QM,2)`, *p* < 0.001). Across exercise modalities, the bias-corrected estimate of effect (*g* = `r round(coef(pub_bias_corrected)[1],2)`) was smaller than an uncorrected estimate (*g* = `r round(coef(overall_ex_model)[1],2)`). Pooled effects remained significant when only including non-significant studies (see SXXX). As a result, no amount of publication bias would be sufficient to nullify effects (*s* = "Not possible"). To reduce effects below -0.2, significant studies would need to be reported `r round(s_value$stats$sval_est,0)` times more frequently than non-sigificant studies.



```{r}

score_reviewer_3 <- function(rob_col){
  # rob_col <- ex_control_pairwise$selective_reporting
  rob_col <- case_when(
    rob_col == "High risk" ~ 3,
    rob_col == "Unclear risk" ~ 1,
    rob_col == "Low risk" ~ 0
  )
  rob_col
}

rev3_rob_data <- ex_control_pairwise
rev3_rob_data[, rob_criteria] <- lapply(rev3_rob_data[, rob_criteria], score_reviewer_3)

rev3_rob_data$overall <- rowSums(rev3_rob_data[, rob_criteria])

if(!exists("moderate_by_rev3_rob")){
  moderate_by_rev3_rob <- brm(TE | se(seTE) ~ 1 + overall + (1 | studlab),
                                         data = rev3_rob_data,
                                         control = list(adapt_delta = 0.99,
                                                        max_treedepth = 15),
                                         cores = 8, chains = 8,
                                         iter = 6000,
                                         prior = priors, silent = 2)
  saveRDS(moderate_by_rev3_rob, "moderate_by_rev3_rob.RDS")
}

rev3_plot <- conditional_effects(moderate_by_rev3_rob)
rev3_plot <- clean_names(rev3_plot$overall)


# Plotting dose-response relationship between exercise dose (METs-min/week) and effect size (SMD) 
rev3_overall_plot <- ggplot(rev3_plot, aes(x = overall,
                                    y = estimate,
                                    ymin = lower,
                                    ymax = upper)) +
  geom_ribbon(alpha = 0.3) + 
  geom_line(colour = "#0C869B") + 
  labs(x = "Total for study risk of bias (for each criteria low=0, moderate=1 and high=3)",
       y = "Predicted effect size (g)",
       fill = "Credible interval") +
  # scale_x_continuous(limits = c(1, 8.5),
  #                    breaks = seq(1,8,1)) +
  plot_theme
rev3_overall_plot
ggsave(filename = "figs/Total for study risk of bias scoring via Reviewer 3 suggestion.png",
        plot = rev3_overall_plot,
       width = 10, height = 6)
```
